\mytitle

### 2020-05-21 paper.tex
Figures and Fujitsu.

In this section, we 
present an empirical evaluation of the two quadratic models based on 
12 standard WFLO instances.
Our main results are: \begin{itemize}
	\item \quls{} when solved using the digital annealer (DA) achieves a solution quality as good or better than the state-of-the-art exact methods on 10 of 12 instances.
		\item To achieve such a solution quality, the runtime for solving \quls{} on the DA is at least two orders of magnitude lower than \qcls{} for hard WFLO instances.  
	\item Given sufficient runtime, solving the \qcls{} model yields strong results on most of the instances. Compared to previous exact models (such as \qcss), \qcls{} is able to find equal or better solutions on 8 of 12 benchmark problems and for 5 of the 6 hard scenarios. %  \todo{Arik: Is this correct? Table 2 shows DA@10seconds with the best solution found for 7/12 instances and \qcls{}grb@3600 for 6/12. And 4/6 vs. 3/6 for the WR36). Are you comparing \qcls{}grb with \qcssgrb and ILP-LS? We seem to be underplaying DA performance in this comment. Chris: I changed to competitive results. You're right, I'd say that the DA is not `losing' to \qcls{}grb.}  
\end{itemize}

>>>>

In this section, we 
present an empirical evaluation of the two quadratic models based on 
12 standard WFLO instances.
Our main results are: \begin{itemize}
	\item \quls{} when solved using the Digital Annealer (DA) achieves a solution quality as good or better than the state-of-the-art exact methods on 10 of 12 instances.
		\item To achieve such a solution quality, the runtime for solving \quls{} on the DA is at least two orders of magnitude lower than \qcls{} for hard WFLO instances.  
	\item Given sufficient runtime, solving the \qcls{} model yields strong results on most of the instances. Compared to previous exact models (such as \qcss), \qcls{} is able to find equal or better solutions on 8 of 12 benchmark problems and for 5 of the 6 hard scenarios. %  \todo{Arik: Is this correct? Table 2 shows DA@10seconds with the best solution found for 7/12 instances and \qcls{}grb@3600 for 6/12. And 4/6 vs. 3/6 for the WR36). Are you comparing \qcls{}grb with \qcssgrb and ILP-LS? We seem to be underplaying DA performance in this comment. Chris: I changed to competitive results. You're right, I'd say that the DA is not `losing' to \qcls{}grb.}  
\end{itemize}
